### 2018-04-02 dissertation/3-vanets/chapter3.tex
updated chapters 3, 4, 5

\section{Special properties of VANETs}
%As was described above, VANETs are a special type of MANETs, which in turn are technological networks.
%However, 
VANETs feature several unique properties which distinguish them, and the behavior of its members, from other types of networks \citep{yousefi2006vehicular}.
Some of these properties include:

@@

The ART model proposed in \citep{li2016art} works in two main steps: data gathering and malicious node detection.
It uses the Dempster-Shafter theory of evidence to merge data coming from other nodes.
Then, it uses a Cosine-based metric to compare two nodes' trust vectors (a series of opinions regarding other nodes).
However, these steps require several intensive calculations, which greatly increase the complexity of the algorithm.
The authors present no details on how it deals with sparsity, dynamics, scalability, security and privacy.
%extend

>>>>

\section{Special properties of VANETs}
\label{section:properties}
%As was described above, VANETs are a special type of MANETs, which in turn are technological networks.
%However, 
VANETs feature several unique properties which distinguish them, and the behavior of its members, from other types of networks \citep{yousefi2006vehicular}.
Some of these properties include:

@@

The Attack-Resistant Trust Management Scheme (ART) from \citep{li2016art} proposes to resist three types of attacks: 
simple attacks, in which malicious nodes do not cooperate with the network;
bad-mouth attacks, in which malicious nodes perform simple attacks but also share false information about benign nodes;
and zig-zag attacks, in which nodes vary their behaviour from benign to malicious in order to be harder to detect.
It works in two main steps: data gathering and malicious node detection.
For data gathering, it uses the Dempster-Shafter theory of evidence, which establishes \textit{belief} and \textit{plausibility} values, both real numbers ranging from 0 to 1.
The former refers to the amount of evidence indicating the truthfulness of a hypothesis (for example, a node sending false data corroborates the hypothesis of it being malicious), while the latter is 1 minus the amount of evidence that supports the possibility of the hypothesis being false.
These evidences are acquired through observations by a node and through data received from other nodes.
The resulting probability is the basic trust value, which is stored in a trust vector (a series of trust values regarding other nodes).
The malicious node detection step uses a Cosine-based metric to compare two nodes' trust vectors.
When two nodes share similar opinions about other nodes, they will consider each other trustworthy.
The downside of this model is that each step is mathematically costly, requiring several intensive calculations in order to achieve its goals.
This likely increases the complexity of the algorithm, which is not detailed by the authors.
Because of this, it is uncertain how the model would scale to large networks, while it might also underperform in small networks in which there is little evidence to collect.
%The authors present no details on how it deals with sparsity, dynamics, scalability, security and privacy.
%extend

### 2018-04-02 dissertation/4-project/chapter4.tex
updated chapters 3, 4, 5

@@

\begin{enumerate}
	\item Node $u$ checks which are its neighbors (nodes within its communication range).
		  New discovered nodes and new formed edges are added to $T^u_i$.
		  Edges are created with weight 0.5.
	\item Node $u$ tests all its neighbors to discover which ones can be directly trusted or not.
		  New trust values are computed for the edges using the average between the previous value and either 1 (if the neighbor is trustworthy) or 0 (otherwise).
	\item If a neighbor $v$ is trustworthy, $u$ merges $T^v_{i-1}$ into $T^u_i$.
	\item Tarjan's algorithm is executed to identify the strongly connected components of $T^u_i$, resulting in a component graph $C^u_i$.
	\item The graph coloring algorithm is executed on $C^u_i$ and nodes are classified as benign or malicious.
\end{enumerate}

>>>>

In a network in which malicious nodes are a minority (under 50\%), it is expected that the benign nodes will form components with large numbers of nodes, because these benign nodes will share their networks with each other and it is easy to form trust paths between pairs of benign nodes.
Malicious nodes, on the other hand, do not send their own networks of false information to benign nodes, and might not always trust other malicious nodes, causing them to become isolated in small strongly connected components (in some cases, these contain a single malicious node).
The result is that most benign nodes become members of a small number of large components; when the component graph is colored, these components are likely to receive the same color, because two benign components are never adjacent.
Because of this, the coloring heuristic works as a classification method.
%Classifying the color that represents the most nodes as correct works because

@@

\begin{enumerate}
	\item Node $u$ checks which are its neighbors (nodes within its communication range).
		  New discovered nodes and new formed edges are added to $T^u_i$.
		  Edges are created with weight 0.5.
	\item Node $u$ tests all its neighbors to discover which ones can be directly trusted or not.
		  New trust values are computed for the edges using the average between the previous value and either 1 (if the neighbor is trustworthy) or 0 (otherwise).
	\item If a neighbor $v$ is trustworthy, $u$ performs a union with $T^u_{i-1}$ and $T^v_{i-1}$, establishing $T^u_i$.
	\item Tarjan's algorithm is executed to identify the strongly connected components of $T^u_i$, resulting in a component graph $C^u_i$.
	\item The graph coloring algorithm is executed on $C^u_i$ and nodes are classified as benign or malicious.
\end{enumerate}

### 2018-04-02 dissertation/5-simulations/chapter5.tex
updated chapters 3, 4, 5

As a comparison, the city of São Paulo (Brazil), which has a fleet of over 8 million vehicles \citep{saopaulofleet} in an area of 1,521.11 km\textsuperscript{2} \citep{saopauloarea}, has a density of 0.8884 at $\rho = 10$m, a much higher value than what is necessary for a satisfactory performance of the algorithm.
\autoref{table:citydensities} shows the densities of a few major cities around the world, using $\rho = 10$m for all of them.
All data is taken from local government sources regarding the number of licensed vehicles in each city; these numbers do not include vehicles from the larger metropolitan aras that surround these cities.
%Areas are shown in km\textsuperscript{2} (values were converted to m\textsuperscript{2} for calculation).

@@

@@

>>>>

As a comparison, the city of São Paulo (Brazil) has a fleet of over 8 million vehicles \citep{saopaulofleet} in an area of 1,521.11 km\textsuperscript{2} \citep{saopauloarea}, and thus has a density of 0.8884 at $\rho = 10$m, a much higher value than what is necessary for a satisfactory performance of the algorithm.
\autoref{table:citydensities} shows the densities of a few major cities around the world, using $\rho = 10$m for all of them.
All data is taken from local government sources regarding the number of licensed vehicles in each city; these numbers do not include vehicles from the larger metropolitan areas that surround these cities.
%Areas are shown in km\textsuperscript{2} (values were converted to m\textsuperscript{2} for calculation).

@@

Simulations of TruMan were performed with densities as low as 0.0017, a value much lower than even the real world density of Helsinki, which is a city with relatively few vehicles for its size.
It can be expected that the model will perform even better in real-world scenarios in cities with even higher densities, which is common, as exemplified by \autoref{table:citydensities}.

@@

\section{Satisfaction of desired properties}
\label{section:satisfaction}

Eight desired properties for VANET trust models were presented in \autoref{section:properties}.
Here, TruMan's ability to satisfy each property is evaluated, ending with a final comparison between TruMan and previously proposed trust models for VANETs.
